\noindent\fcolorbox{black}{gray}{\makebox[\textwidth][l]{\textcolor{white}{\textsc{\textbf{Description of the proposed research}}}}}

\invisiblesection{Research topic}
\textit{Maximum 2,000 words for sections 7a an 7b together, including footnotes and illustrations but excluding literature references. See also the description of the criteria for full proposals in the call for proposals (paragraph 4.2.2).}

\subsection{Research topic}\label{restop}

\subsection{Approach}\label{appl}

\subsection{Word count (sections \ref{restop} and \ref{appl})}

\begin{tabular}{|c|c|c|c|}
\hline
&&& \\
\hline
\end{tabular}

\subsection{Time plan}
\textit{Give a practical timetable over the grant period, max. half a page.}

\subsection{Dissertation, scientific output including data and output related knowledge utilization}

\begin{tabular}{|c|p{5cm}|c|l|}
\hline
	& Output & Number & Expected year of publication \\
\hline
	$\Box$ & Articles in refereed journals && \\
\hline
	$\Box$ & Articles in non-refereed journals && \\
\hline
	$\Box$ & Books && \\
\hline
	$\Box$ & Book chapters && \\
\hline
	$\Box$ & Dissertation && \\
\hline
	$\Box$ & Conference papers && \\
\hline
	$\Box$ & Data (see also question \ref{data}) && \\
\hline
	\multicolumn{4}{|l|}{\textbf{Output related to knowledge exchange and impact (please specify)}} \\
\hline
	$\Box$ & Professional publications && \\
\hline
	$\Box$ & Other scientific output && \\
\hline
	$\Box$ & Publications aimed at general public && \\
\hline
\end{tabular}

\subsection{Knowledge exchange and impact}
\textit{Address the potential for and implementation of knowledge exchange and impact (Max. 500 words and no more than 1 page, for assistance see paragraphs 4.2.2 and 6.2 of the call for proposals) Potential}
\begin{itemize}
	\item[-] \textit{Describe what the project’s contribution will be to society and/or to other scientific domains;}
	\item[-] \textit{Describe who will benefit from the project’s results and why;}
\end{itemize}

\textit{Implementation}
\begin{itemize}
	\item[-] \textit{Describe how the project’s results will be disseminated to potential users;}
	\item[-] \textit{Describe, if available, the project team’s expertise on knowledge exchange and impact and how it will be deployed to enhance knowledge exchange and impact of results;}
	\item[-] \textit{Describe how potential users of the project’s results will be included;}
	\item[-] \textit{Describe when the project’s result are ready for use by third parties within and outside the academic sector.}
\end{itemize}

\textit{In the case of research that does not lend itself to knowledge utilisation as described in the aforementioned terms, the applicant is requested to briefly explain why he/she believes that knowledge utilisation is not applicable to the proposed research. In that case you do not need to address implementation. Please be aware that knowledge exchange and impact may always be a point of discussion during the interview.}

\subsection{Literature references}
\textit{Maximum 35 references}